Methods and Results

### 2022-10-04 ms.Rmd
getting lnSD model up

    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()

@@

       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
        final_long <- left_join(final_long1, data_long_n, by = "obs")

>>>>

    data_long <- data %>% filter(geary_test == "pass") %>%  
                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
                data.frame()

@@

       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
        final_long <- left_join(final_long1, data_long_n, by = "obs") %>% 
                      rename("sd" = value.y,
                             "mean" = value.x,
                             "n"  = value,
                             "trt" = name.x) %>% 
                      mutate(trt = factor(trt))

    # Now that we have it in long format, we can calculate lnSD and lnX and their associated SE's

        final_long <- escalc(sdi = value.y, ni = value,  
                             measure = "SDLN", data = final_long, 
                             append = TRUE, var.names=c("lnSD","v_lnSD"))

         final_long <- escalc(mi = value.x, sdi = value.y, ni = value,  
                              measure = "MNLN", data = final_long, 
                              append = TRUE, var.names=c("lnX","v_lnX"))

    # Fit a MLMA model with metafor
        model1_lnSD <- rma.mv(lnSD ~ 1 + name.x + lnX, V = v_lnSD, 
                       random = list(~1 + name.x|study, 
                                     ~1|obs, 
                                     ~1|species), 
                       dfs = "contain", test = "t", 
                       method = "REML", data = final_long)
